manuscript

### 2025-02-01 doc/Manuscript.qmd
update introduction

The well-documented decline of the endangered Sierra Nevada yellow-legegd frog in its namesake mountain range (bunch of citations) is emblematic of the crisis facing amphibians globally (citations). As is the case with numerous other species...the fungal pathogen Bd is the primary driver of SNYLF decline in the Sierra Nevada (citations), and the effects of climate change loom large-yet remain understudied- especially in an alpine environment expriencing accelerated climate change (mountain ranges are warming faster than other places?) (citation).

>>>>

The well-documented decline of the endangered Sierra Nevada yellow-legegd frog in its namesake mountain range (bunch of citations) is emblematic of the crisis facing amphibians globally (citations). As is the case with numerous other species...the fungal pathogen Bd is a primary driver of SNYLF decline in the Sierra Nevada (citations), and the effects of climate change loom large-yet remain understudied- especially in an alpine environment expriencing accelerated climate change (mountain ranges are warming faster than other places?) (citation).

-   get rid of climate *change* here. Introduce just climate somewhere in the intro, then get into climate *change* later, like int he discussion.
